%-------------------------
% Resume in Latex
% Author: Md. Sakib Hasan
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

%-------------------------
% Custom Commands

\newcommand{\resumeItem}[1]{
  \item\small{#1\vspace{-2pt}}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small #3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeProjectHeading}[2]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \small #2 \\
    \end{tabular*}\vspace{-6pt}
}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in,label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}

\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
\begin{document}

\begin{center}
{\Huge\bfseries Md. Sakib Hasan}\\[4pt]

\small
+880-177-735-4458 $|$
\href{mailto:sakib.hsn44@gmail.com}{sakib.hsn44@gmail.com}
$|$
\href{https://www.linkedin.com/in/sakibhasan-dev/}{LinkedIn}
$|$
\href{https://github.com/Pro-seka}{GitHub}
$|$
\href{https://pro-seka.github.io/sakib-os}{Portfolio}
\end{center}

%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart

\resumeSubheading
{Daffodil International University}{Dhaka, Bangladesh}
{B.Sc. in Software Engineering}{Jun. 2024 -- Jun. 2028}

\resumeSubheading
{Rajbari Government College}{Rajbari, Bangladesh}
{Higher Secondary Certificate (Science)}{Jan. 2021 -- Jan. 2023}

\resumeSubHeadingListEnd

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
\resumeSubHeadingListStart

\resumeItem{\textbf{Languages:} C, Python, Java, JavaScript, SQL, Bash}
\resumeItem{\textbf{Frameworks \& Libraries:} React, Node.js, Express, Flask, Streamlit, Pandas, NumPy, Scikit-learn, OpenCV, YOLO, MediaPipe}
\resumeItem{\textbf{Databases:} SQLite, MongoDB, MariaDB}
\resumeItem{\textbf{Tools \& Technologies:} Git, GitHub, Docker, Linux, Oracle Cloud, Vercel, Supabase}
\resumeItem{\textbf{Core Competencies:} Full-Stack Development, AI Integration, Machine Learning, Computer Vision, System Design}

\resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
\resumeSubHeadingListStart

\resumeProjectHeading
{\textbf{ClusterPilot} $|$ Python, Kubernetes, Docker, Prometheus, Redis}{Jan. 2026 -- Present}
\resumeItemListStart
\resumeItem{Built an autonomous GPU resource-optimization platform for Kubernetes-based AI clusters.}
\resumeItem{Implemented idle-GPU forecasting, safe resource reclamation, and priority-based workload scheduling.}
\resumeItem{Developed real-time dashboards for GPU utilization, cost analytics, and cluster management.}
\resumeItemListEnd

\resumeProjectHeading
{\textbf{TrashHawk} $|$ Python, Flask, YOLO, OpenCV}{Oct. 2025 -- Present}
\resumeItemListStart
\resumeItem{Developed an AI-powered waste-monitoring system that detects littering violations from surveillance footage using YOLO and OpenCV.}
\resumeItem{Built an offline video-analysis and automated evidence-reporting pipeline for flagging violations.}
\resumeItem{Secured university funding to advance the project from prototype to deployment.}
\resumeItemListEnd

\resumeProjectHeading
{\textbf{ColabCore} $|$ React, Node.js, Python, MongoDB, Scikit-learn}{2026 -- Present}
\resumeItemListStart
\resumeItem{Developed an AI-powered platform connecting students, universities, and recruiters through intelligent opportunity matching.}
\resumeItem{Built ML recommendation and NLP pipelines for resume parsing, semantic skill extraction, and personalized recommendations.}
\resumeItem{Developed role-based dashboards for placement tracking, analytics, and industry skill-demand forecasting.}
\resumeItemListEnd

\resumeProjectHeading
{\textbf{SakibAI} $|$ Python, Streamlit, SQLite, Ollama, OpenAI API}{2026 -- Present}
\resumeItemListStart
\resumeItem{Developed a modular AI workspace integrating Ollama, OpenAI, Groq, and Together AI through a unified interface.}
\resumeItem{Built document intelligence, an AI study assistant, and a personal knowledge base with local document search.}
\resumeItem{Engineered a privacy-first architecture with SQLite persistence, Docker deployment, and multi-format export support.}
\resumeItemListEnd

\resumeSubHeadingListEnd

%-----------LEADERSHIP & ACHIEVEMENTS-----------
\section{Leadership \& Achievements}
\resumeSubHeadingListStart

\resumeProjectHeading
{\textbf{Co-Founder, Thirst For Science}}{Apr. 2019 -- Jul. 2024}
\resumeItemListStart
\resumeItem{Co-founded a STEM outreach community, organizing workshops and competitions that engaged young learners through hands-on physics experiments.}
\resumeItem{Secured funding from sponsors to support club events.}
\resumeItemListEnd

\resumeProjectHeading
{\textbf{Debating \& Science Olympiads}}{}
\resumeItemListStart
\resumeItem{Won multiple district-level championships in Classical and Parliamentary debate.}
\resumeItem{Multiple-time national award recipient in Mathematics and Physics Olympiads.}
\resumeItemListEnd

\resumeSubHeadingListEnd

\end{document}
